Seeing Double: Indications From {\it TESS} and {\it Gaia} That PTFO$\,$8-8695b is Not a Planet

### 2020-04-17 paper/ms.tex
make HR diagram even better

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf HR diagram of \ptfo\ and late-type members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  We defined the reference
  ``neighborhood'' (gray circles) as the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  $G$ is the Gaia broadband, $Bp$ is Gaia blue, $Rp$ is Gaia red, and
  $\omega_{\rm as}$ is the parallax in arcseconds.
  The $x$-axis limits have been set to show only K and M dwarf
  members, to accentuate \ptfo's separation from the
  single-star sequence.
	\label{fig:gaia}
	}
\end{figure*}

>>>>

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Hertzsprung-Russell diagram of \ptfo\ and late-type members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  The reference
  ``neighborhood'' (gray circles) is the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  It contains members of the full Orion complex with a wider spread of ages,
  in addition to field interlopers.
  $G$ is the Gaia broadband, $Bp$ is Gaia blue, $Rp$ is Gaia red, and
  $\omega_{\rm as}$ is the parallax in arcseconds.
  The $x$-axis limits have been set to show only K and M dwarf
  members, to accentuate \ptfo's separation from the
  single-star sequence.
	\label{fig:gaia}
	}
\end{figure*}
